\documentclass{article}
\begin{document}

\title{Topic 1 Outline}
\author{group 27}

\maketitle
\newpage

\section{Background research}
We split our group into 3 sub-groups, each sub-group focusing on one of the 3 topics we have chosen (text messages,
photos and videos). We will all look at what each subtopic does to create Dark Data, where it is stored, and the
consequences of them.

\section{Topics}
    \subsection{Text Messages} 
        \subsubsection{Members}
        \begin{itemize}
            \item \textbf{Jacob} - Will focus on why text messages produce a lot of Dark Data, covering all the 
            possibilities and each of their impacts and finding out how much Dark Data is being produced simply from text 
            messages.
            \item \textbf{Aaron} - will look in to the dark data around softwere based logging and other texutal output from softwere.

        \end{itemize}
        \subsubsection{Description}
        Text messages can be considered \textbf{dark data} because of their permanent nature they are stored in (the cloud) and 
        are normally kept well after they are sent and received. This means a lot of data has to be saved to be able to
        store the communications in large quantities of people's records. 
    \subsection{Photographs}
        \subsubsection{Members}
        \begin{itemize}
            \item \textbf{Mathew}
            \item \textbf{Hamza}
        \end{itemize}
        \subsubsection{Description}
        Photos can be considered \textbf{dark data} as many people take lots of photos to capture a precious moment. However, these photos stack up over time and the amount of photos can range from hundreds to the millions. This means there must be lots of data storage in order to store the photos.
        I will research the consequences of the data storage of photos.

    \subsection{Video}
        \subsubsection{Members}
        \begin{itemize}
            \item \textbf{Kacper} - Will focus on dark data which is generated specifically from social media apps, Instagram, Tiktok and Snapchat. Along with researching the impact of generative AI, when
            content is mass produced.
            \item \textbf{Ryan}
        \end{itemize}
        \subsubsection{Description}
        We will study on how much data the group generates, specifically with videos. We will carry extensive research on Snapchat, Instagram, and TikTok and record how much Dark Data they produce, along with these apps using AI-generated content, as this type of media has a lot of AI usage.

        \subsubsection{Overview}
        There is an enormous amount of content being uploaded and being accessed via the internet, mostly from large video 
        streaming companies and social media companies like Netflix, YouTube, and Twitch. Our group will research
        how this is stored and the consequences of having to store so much data. We will also look into how Businesses can
        take/produce loads of Dark Data to be able to benefit their organizations overall performance.

        \subsubsection{Points}
        \begin{itemize}
            \item How much data is being stored by these companies.
            \item The environmental consequences of storing Dark Data.
            \item The materials required to build the infrastructure to support such large data storage facilities.
            \item The impact that has on companies, countries, and the ethical consequences.
            \item The future of these companies and how they'll choose to store and deliver this data.
            \item How consumers use these services.
        \end{itemize} 

\subsection{Milestones}
    \begin{itemize}
        \item \textbf{Topic 1: Stage 1, Assignment 1} - 1pm, 09/10/24
        \item \textbf{Finish topic research} - 15/10/24
        \item \textbf{Topic 1: Stage 2, Assignment 1} - 10am, 22/10/24
        \item \textbf{Finish HTML} - 23/10/24
        \item \textbf{Topic 1: Stage 3, Assignment 1} - 10am, 29/10/24
    \end{itemize}

\end{document}
